SMT-Boosted Security Types for Low-Level MPC

### 2024-10-10 esop25/cpj.tex
checkpoint

\begin{lemma}
  Given $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$,
  for all $x \in S \cup R$ and $M \subseteq V$ exactly one of the following conditions holds:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\setit{x}$ interferes with $M$.
  \item There exists $X \subseteq S \cup R$ such that $\setit{x} \cup X$ interferes
    with $M$ but neither $X$ nor $\setit{x}$ alone do, in which case we say
    that $\setit{x}$ interferes with $M$ conditionally on $X$.
  \item Neither condition (i) nor (ii) hold.
  \end{enumerate}
\end{lemma}

@@

Our main type soundness result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\begin{theorem}
  \label{theorem-cpj}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and for all $H,C$ we have $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T = \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemma \ref{lemma-cpjsound}. \qed
\end{proof}

>>>>

\begin{lemma}
  \label{lemma-interference}
  Given $\prog$ with $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$,
  for all $x \in S \cup R$ and $M \subseteq V$ exactly one of the following conditions holds:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\setit{x}$ interferes with $M$.
  \item There exists $X \subseteq S \cup R$ such that $\setit{x} \cup X$ interferes
    with $M$ but neither $X$ nor $\setit{x}$ alone do, in which case we say
    that $\setit{x}$ interferes with $M$ conditionally on $X$.
  \item Neither condition (i) nor (ii) hold.
  \end{enumerate}
\end{lemma}

@@

Our main type soundness result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\begin{theorem}
  \label{theorem-cpj}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and for all $H,C$ we have $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T = \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemmas \ref{lemma-cpjsound} and \ref{lemma-interference}. \qed
\end{proof}
